---
title: "The Effectiveness of Psychotherapy Delivered in Routine Care Settings: A Systematic Review and Meta-Analysis"
author: "Chris Gaskell"
date: "`r Sys.Date()`"
output:
  html_docucment: default
  word_document:
    reference_docx: my-styles.docx
  bookdown:: pdf_book
  pdf_document:
    citation_package: default
    toc: false
    toc_depth: 1
    keep_tex: yes
fontsize: 12pt
indent: true
bibliography:
- bib/book.bib
- bib/packages.bib
- bib/LiteratureReview.bib
- bib/Jaime.bib
csl: reference-style/apa7.csl
classoption: openany
always_allow_html: yes
description: This document reports the results of a meta-analysis on naturalistic
  psychotherapy outcomes
documentclass: book
github-repo: rstudio/bookdown-demo
subparagraph: yes
header-includes:
link-citations: yes
biblio-style: apalike
site: bookdown::bookdown_site
geometry: "left=2cm, right=2cm, top=2cm, bottom=2cm"
editor_options: 
  markdown: 
    wrap: 72
---

```{r packages, include=FALSE, warning=F, message=F}
# Bookdown
library(bookdown)
library(servr)
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
library(rmarkdown)
library(knitr)
# Meta-analysis
library(metafor)
library(meta)
library(dmetar)
library(PRISMAstatement)
# Data manipulation
library(tidyverse)
library(rstatix)
library(readxl)
library(foreign)
library(summarytools)
library(haven)
library(labelled)
# Tables
library(janitor)
library(kableExtra)
# Other
library(irr)

# Global Environemnt Options
options(scipen = 99999)
options(warn = 1)
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

# Set WD
"/Users/chris/Documents/thesis-meta-submission/psychotherapy-research/submission-2/effectiveness-meta"
```

```{r data-input, echo=FALSE, include=FALSE}
source("scripts/funs.R")
source("scripts/cleaning.R")
source("scripts/res.R")
source("scripts/tabs.R")
source("scripts/mod-tab.R")
```

```{r write-bib, include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Abstract {#Abstract .unnumbered}

**Objective:** Most psychotherapy is delivered in naturalistic settings. There has been a substantial increase in recent decades in the amount of evidence generated by routine services and so this review sought to examine the effectiveness of routinely delivered psychological therapies.

**Method:** A pre-registered systematic-review and random-effects meta-analysis on studies meeting pre-specified inclusion criteria was conducted (CRD42020175235). Between-study heterogeneity was explored using methodological and clinical variables in univariate and multivariate moderator analyses.

**Results:** The systematic search identified
`r dat.mod %>% filter(StudySampleN == 1) %>% nrow()` studies
(*k* = `r dat.mod %>% nrow()` samples), of which 
`r dat.mod %>% filter(StudySampleN == 1 & For.Meta == "Yes") %>% nrow()` (*k* = `r dat.mod %>% filter(For.Meta == "Yes") %>% nrow()` samples) were
eligible for inclusion in the meta-analysis.
Results showed large effects for
depression
(*d* = `r round(res$rma$dep$b, 2)`,
[CI `r round(res$rma$dep$ci.lb, 2)`-`r round(res$rma$dep$ci.ub, 2)`],
*p* = `r format.pval(res$rma$dep$pval, eps = .001)`,
*k* = `r res$rma$dep$k`),
anxiety
(*d* = `r round(res$rma$anx$b, 2)`
[CI `r round(res$rma$anx$ci.lb, 2)`-`r round(res$rma$anx$ci.ub, 2)`],
*p* = `r format.pval(res$rma$anx$pval, eps = .001)`,
*k* = `r res$rma$anx$k`),
and miscellaneous outcomes 
(*d* = `r round(res$rma$gen$b, 2)`
[CI `r round(res$rma$gen$ci.lb, 2)`-`r round(res$rma$gen$ci.ub, 2)`],
*p* = `r format.pval(res$rma$gen$pval, eps = .001)`,
*k* = `r res$rma$gen$k`).
Continent was the only significant moderator of treatment effects across all outcome domains. 

**Conclusion:** This review provides support for the effectiveness of routinely delivered psychological therapy. Findings should be interpreted with caution due to the observational nature of effectiveness studies and also the marked heterogeneity shown across study designs and characteristics.

**Keywords:**
'Psychotherapy', 'Effectiveness', 'Naturalistic', 'Routine Outcomes',
'Meta-analysis'.

**Clinical Significance of this Article:**
The present study is the most comprehensive systematic review and meta-analysis of outcome data from practice-based psychotherapy studies. Pooling data from various countries, clinical contexts, therapy modalities and outcome measures, this study provides robust evidence that routinely delivered psychological interventions are effective for the treatment of depression, anxiety and global psychological distress, with large effect sizes across these domains (*d* > .80). Psychological treatments delivered in naturalistic settings are broadly effective for the alleviation of common indicators of psychological distress.

